\pagebreak
\section{Changes from Previous Versions}

%No previous versions yet.  

% these would be subsections "Changes from v. WD-..."
% Use itemize environments.
\subsection{Changes from PR-2022-06-21}
\begin{itemize} 
  \item Corrected titles on Vocabulary references in Appendix C.
  \item Corrected order of listing these history comments (newest first).
\end{itemize}
\subsection{Changes from PR-2020-03-10}
\begin{itemize} 
  \item Restored Point subclasses: CartesianPoint, LonLatPoint, GenericPoint
  \item Removed 'default' listing of dependent vocabularies from Appendices.
  \item Update citation tags for IVOA standards.
  \item Revision to the Use Case section in response to RFC comments.
\end{itemize}
\subsection{Changes from PR-2019-08-30}
\begin{itemize} 
  \item Migrate CoordSys element to include both CoordSpace and CoordFrame concepts.
  \item Coordinate element to reference CoordSys, rather than CoordFrame and CoordSpace.axis
  \item Removed specialized Coordinate types linked to standard spatial coordinate spaces, replace with Point
  \item Corrected multiplicity of SpaceFrame.planetaryEphem
  \item Corrected URLs for vocabularies ('http' not 'https')
  \item Corrected LaTex for TCG and TCB records to fix display 
\end{itemize}
\subsection{Changes from WD-2019-03-20}
\begin{itemize} 
  \item Section 1.2: added clarifying text on the distinction between Quantity, Coordinate, and Measurement in the IVOA models.
  \item Updated URLs for vocabularies
  \item Appendix B: changed 'Class' to 'ObjectType' to better align with the VO-DML description.
  \item Appendix C: brought initial vocabulary content in line with URL content.
\end{itemize}
